Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1231 at $z$=0.654

### 2016-06-21 WRITEUP/ms.tex
replace dyn mass calc with disk model instead of from virialized

%--------------------------------------------------------------------------
%                                Analysis
%--------------------------------------------------------------------------
\section{Analysis} \label{sec:anal}
\subsection{Lens modeling} \label{sec:lensmodel}
At the angular resolution of the \bco data, the images are resolved over
$\sim$2 resolution elements. Given the extent of the lensed emission,
this implies that our \bco observations do not resolve
structures (e.g. knots and arcs) of the lensed emission
(i.e., sub-optimal for
performing lens modeling). Nevertheless, the high spectral
resolution of this data provides dynamical information on
spatial scales smaller than the beam (see \Fig{CO21highO}).
Hence, with the high SNR, we reconstruct the intrinsic gas
dynamics by carrying out a parametric lens modeling over different
channel slices of the interferometric data using our lensing code
\uvmcmcfit (\citealt{uvmcmcfit15a}; see \citealt{Bussmann15a} for details of
the code). Models of each slice thus provide the
properties on the intrinsic kinematics. To increase the SNR for modeling, the
slices are obtained by binning five native channels
($\Delta v$\,$\sim$\,21.5\kms) over the full
linewidth of $\sim$750\,\kms in the original data, resulting in seven
independent channels.

@@

\subsubsection{Interpretation of the source-plane morphology} \label{sec:caveat}
The reconstructed source locations in \Fig{model} demonstrate
an intrinsic velocity gradient across the source plane, which is
indicative of a kinematically-ordered disk-like galaxy. 
Additional support to the disk conjecture
can be found in the double-horned line profile (\Fig{CO21spec})
and the observed (image plane) velocity field (\Fig{CO21highO}). Furthermore,
C06 also find that the reconstructed source plane emission in optical-NIR
is best-reproduced using a $n$\,=\,1 Sersic profile.
We thus interpret RXJ1131 to be a disk galaxy.

% the companion
One other interesting result from our lens model is that a better fit is
found for the red-most channel if we add a second source component (see
top left panel in \Fig{model}). This is consistent with previous results
reported by \citet{Brewer08a}, who find an optically faint companion
(component F in their paper) $\sim$2.4\,kpc away from the AGN host galaxy,
and C06, who find evidence for an interacting galaxy near RXJ1131.
Spatially, the red velocity component of the CO emission
also coincides with this component F. It is therefore evident that we
detect \bco emission in the companion galaxy.
To quantify the type of merger (major v.s. minor) conventionally with a mass
ratio, we decompose the total line flux into two components:
one from RXJ1131 and the other from its companion.
Since the companion is only detected in the red-most channel, we
use the best-fit flux densities and magnification factors obtained
from the model of this channel to derive the intrinsic gas mass in the companion.
Without direct \rot{1}{0} measurements, we derive \rot{1}{0} intensity
assuming a brightness temperature ratio of $r_{\rm 21}$\,=\,1, which was chosen
solely to facilitate a comparison with other U/LIRGs. 
% also ULIRGs are found to be thermalized up to Jup = 3 or 4, but not needed to say here
For the same reason, we adopt a luminosity-to-mass conversion factor of
\alphaco\,=\,0.8 (K \kms pc$^2$)\pmOne. This yields a gas mass
$M_{\rm gas}$ of (1.92\pmm0.09)\,\E{9} \Msun. 
%statistical unc. only (i.e. draw from distributions of on mag. factor & intrinsic flux)
For the molecular gas mass in RXJ1131, we derive
its intrinsic line flux over the FWZI linewidth
using the respective magnification
factors listed in \Tab{model}, which to
first order takes into account effect of differential lensing.
This yields $I_{\small \bco}$\,=\,2.93\pmm0.70 Jy\,\kms,
where the uncertainty includes those on
the magnification factors.
Adopting the same brightness temperature ratio and \alphaco\ as
used for the companion, this corresponds to a gas mass of
$M_{\rm gas}$\,=\,(1.38\pmm0.33)\,\E{10} \Msun,
implying a gas mass ratio of $\sim$7:1 between RXJ1131 and its companion.
We thus classify the system to be a ``wet-wet'' minor merger according to
the classification scheme commonly used in literature.

@@

\subsubsection{Spatial extent and differential lensing} \label{sec:differential}
In the image plane shown in  \Fig{CO21mom}, the redshifted component is 
cospatial with the Einstein Ring seen in the
optical image, with most of its apparent flux originating from the lensed arc
in the southeast, whereas the blue component is predominately coming from
solely the lensed arc. To further illustrate this, we show the
channel maps of 21.5\,\kms width and a spatial spectra map of 1\farcs5 resolution in
\Fig{chanmap} and \Fig{spatialSpec}, respectively. The figures
show that emission
is present to the west, peaking toward the lensing arc (black crosses in
\Fig{chanmap}) in the red wing, and shifts to the east with decreasing velocity
(blue wing).
This is consistent with the source plane positions in our models and 
is suggestive of an extended CO emitting region.

@@

\subsection{\bco Dynamical modeling} \label{sec:dynamics} %DONE
Assuming the velocities of the respective channels used in the
lens modeling correspond to solely the tangential component of the
true velocity vector of a rotating disk (i.e., along the major axis),
we extract a one dimensional PV diagram in \Fig{PV}
by slicing across their source plane positions (PA: 121\degr).

@@

In the rest-frame, 
emission in the observed $H$-band corresponds to NIR emission, 
tracing radiation from the accretion disk surrounding
the central AGN and also from old and evolved stellar populations; 
$I$-band corresponds to roughly the optical $V$-band, tracing stellar radiation from
existing, less massive (\ie longer-lasting) stars;
$V$-band corresponds to roughly $U$-band,  tracing radiation from massive young stars 
in the host galaxy. Hence,
the $V$-band compactness may be explained in part
due to the fact that its emission is
more susceptible to dust extinction than in other bands and/or 
a central starburst caused by higher 
concentrations of star-forming gas towards the central regions -- owing to
gravitational perturbations induced
from interactions with the companion
\citep[\eg][]{DiMatteo05a}.
The rest-frame NIR emission is likely to be
dominated by evolved stars since 
the AGN is located at $\sim$0\farcs016 inside the central region % and R_H is 7 kpc
of the host galaxy \citep{Sluse06a}, implying a compact accretion disk. 
This is consistent with the picture that old stars form first and constitute the bulge component  
of a spiral galaxy and that nuclear starbursts are triggered in mergers.

% assuming virialized gas
Using $V_{\rm rot}$ estimate from the modeling, we find a dynamical mass of
$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 17\E{10}\,\Msun enclosed
within the CO-emitting region. If we instead consider the
\bco line peak separation $(\Delta v_{\rm sep}/2 \sim$200\,\kms$)$ as the rotation velocity, we find
$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 5.8\E{10}\,\Msun.
We correct for the inclination effect using the
morphological axial ratio ($a/b\sim$1\farcs8 / 3\farcs25) 
from the reconstructed image (Figure 3 in C06), yielding
an inclination angle of 56.4\degr, which is consistent with the
observed unobscured AGN and an observable double peak line profile.
The dynamical mass is then
8.3\E{10}\Msun\,$<$\,$M_{\rm dyn}$($<$6\,kpc)\,$<$\,25\E{10}\Msun.
Since this quantity is derived under the assumption that the gas is
virialized, which is highly unlikely given the velocity dispersion and the
presence of a close companion, our estimate is
at most an upper limit.

%% using disk model

\subsection{SED modeling} \label{sec:SED}  % DONE
We fit dust SED models to the
24\,\micron$-$2.2\,mm photometry in \Fig{SED}, where we also
include the IRAS 60\,$\micron$ and 100\,$\micron$ upper limits
to constrain the dust peak.
The fit is performed with the code
\ncode{mbb\_emcee} \citep[\eg][]{Riechers13a,Dowell14a}, which samples the posterior
using an MCMC approach and uses instrumental
response curves to perform color correction on-the-fly.
The SED model consists of a modified-blackbody
function with a power-law attached to the
Wien side to account for an excess in the MIR owing to warm,
small dust emission.
% Previous studies find that in the absence of mid-IR data, a powerlaw slope
% of $\alpha$ = 2 is consistent with SB and slightly more shallow, $\sim$1.5, % for SB/AGN composite systems (Blain et al., 2003; Casey, 2012; Koss et al., 2013).
%
%We add $\sim$15\% calibration uncertainties in quadrature to obtain the total
%uncertainties for the PdBI continuum in our fitting procedure.
The model is thus described by five free parameters: the rest-frame characteristic dust
temperature (T$_{d}$), the emissivity index ($\beta$), the power-law index
($\alpha$), the flux normalization at 500\,$\micron$ ($f_{\rm norm}$), and
the observed-frame wavelength at which the emission
becomes optically thick ($\lambda_{0}$). We impose
an upper limit of 100\,K on $T_d$ (commonly BLAH in ULIRGs; CITE), 
a Gaussian prior centered around
$\mu$\,=\,1.9 with $\sigma$\,=\,0.3 on $\beta$, and an upper limit of
1000\,$\micron$ on $\lambda_0$.
We check for chain convergence by requiring the autocorrelation
length of each parameter to be less than the number of steps
taken for the burn-in phase (which are then discarded).
Here we report the means % modes in log file
% summary statistics (global mode (where min. chi),
% marginal mode (in log file), posterior median (instead of posterior means;
% need to compute)
and the 1$\sigma$ confidence interval in the marginal PDFs
as the best-fit parameters, as listed in \Tab{SED}.

@@

\subsection{Gas properties} \label{sec:properties}
In this section, we derive the gas properties of the merger  
based on \bco and compare with those reported by
C13, which is the largest sample of
IR-luminous galaxy at similar redshift
(0.6\,$<$\,$z$\,$<$\,1.0) with CO measurements\footnote{The
\fir luminosity in C13 is derived based on 60\,$\micron$ and 100\,$\micron$ IRAS fluxes,
and using a different definition of
\LFIR: rest-frame 40\,$-$\,500\,\micron. Following this convention, 
we find a \fir luminosity of 
\LFIR = $($8.8\pmm0.4$)$\E{11}$(\mu_{\rm L}$/5.5$)\pmOne$\,\Lsun and
a SFR of $($150\pmm 70$)$\,\sfrU.}.
% the SFR of RXJ1131 is lower (cf. SFR\,$>$\,200 \Msun yr\pmOne, with an average of 1200 in C13).
We note their results are based on \bco and \rot{4}{3} line observations on the single-dish
IRAM 30-m.

\subsubsection{Linewidth \& Sizes} %DONE
We find that the linewidths for both components (redshifted and blueshifted)
inferred from a double Gaussian fit to the line profile are
comparable to the C13 ULIRG sample
($\Delta v_{\rm FWHM}$ of 370\,\kms) and local ULIRGs
(300\pmm85\,\kms; \citealt[][]{Solomon97a}).
Since C13 do not have resolved observations, we compare the
gas distribution with local U/LIRGs. The CO gas in RXJ1131 is
distributed $\sim$6\,kpc in radius across (in
the source plane), which is more extended than the
sample of disk-like U/LIRGs studied by
\citet[hereafter U14]{Ueda14a}, % also classified U/LIRG using FIR from 60, 100 micron measurements
who find an average radius of 3.5\,$\pm$\,2.3\,kpc
with a range spanning 1.1\,$-$\,9.3\,kpc.
% This is expected if the positive correlation in the linewidth-size relation
% holds at intermediate redshifts. Yet we cannot quantify this further
% with the data represented in this paper.

\subsubsection{Gas Mass}
To derive the molecular gas mass, we first correct for lensing magnification
using the respective magnification factors listed in \Tab{model}, which to
first order takes into account effect of differential lensing. This yields
$I_{\small \bco}$\,=\,5.9$\pm$2.7 Jy\,\kms,
where the uncertainty includes those on
the magnification factors.

Without direct \rot{1}{0} measurements,
we derive \rot{1}{0} intensity
using a brightness temperature ratio of $r_{\rm 32}$\,=\,1, which was chosen
solely to facilitate a comparison with other U/LIRGs.
For the same reason, we
adopt a luminosity-to-mass conversion factor of
\alphaco\,=\,0.8 (K \kms pc$^2$)\pmOne, this yields a
CO luminosity \Lp\,=\,(3.47\,$\pm$\,1.58)\E{10}\,\LpU and a gas mass
$M_{\rm gas}$ of (xx\pmm xx)\,\E{10} \Msun. 
BLAH
The inferred gas mass is comparable to
C13 sample ($M_{\rm gas}$\,=\,1.5\E{10}\Msun) as well as
local U/LIRGs \citep{Solomon97a, Sanders96a} but higher than
local LIRGs (U14).

% gas-to-dyn ratio
We place a lower limit on the dynamical mass (see \Sec{dynamics}) using
the inferred gas mass. This BLAH.
 {\bf will need edit depending on the dyn. modeling section}
a gas-to-dynamical mass fraction of $f_{\rm gas-dyn}$\,=\,BLAH.
% gas to dust ratio:
Using the dust mass derived from SED fitting,
we find a gas-to-dust ratio of 184\pmm124, which is consistent with
the C13 sample ($f_{\rm gas-dust}$\,=\,206) and local U/LIRGs
(200$-$350; \citealt{Sanders91a}, Contini \& Contini 2003; Seaquist et al. 2004; Wilson et al. 2008).

>>>>

%--------------------------------------------------------------------------
%                                Analysis
%--------------------------------------------------------------------------
\section{Analysis} \label{sec:anal}
\subsection{Lens Modeling} \label{sec:lensmodel}
At the angular resolution of the \bco data, the images are resolved over
$\sim$2 resolution elements. Given the extent of the lensed emission,
this implies that our \bco observations do not resolve
structures (e.g. knots and arcs) of the lensed emission
(i.e., sub-optimal for
performing lens modeling). Nevertheless, the high spectral
resolution of this data provides dynamical information on
spatial scales smaller than the beam (see \Fig{CO21highO}).
Hence, with the high SNR, we reconstruct the intrinsic gas
dynamics by carrying out a parametric lens modeling over different
channel slices of the interferometric data using our lensing code
\uvmcmcfit (\citealt{uvmcmcfit15a}; see \citealt{Bussmann15a} for details of
the code). Models of each slice thus provide the
properties on the intrinsic kinematics. To increase the SNR for modeling, the
slices are obtained by binning five native channels
($\Delta v$\,$\sim$\,21.5\kms) over the full
linewidth of $\sim$750\,\kms in the original data, resulting in seven
independent channels.

@@

\subsubsection{Interpretation of the Source-plane Morphology} \label{sec:caveat}
The reconstructed source locations in \Fig{model} demonstrate
an intrinsic velocity gradient across the source plane, which is
indicative of a kinematically-ordered disk-like galaxy. 
Additional support to the disk conjecture
can be found in the double-horned line profile (\Fig{CO21spec})
and the observed (image plane) velocity field (\Fig{CO21highO}). Furthermore,
C06 also find that the reconstructed source plane emission in optical-NIR
is best-reproduced using a $n$\,=\,1 Sersic profile.
We thus interpret RXJ1131 to be a disk galaxy.

% the companion
One other interesting result from our lens model is that a better fit is
found for the red-most channel if we add a second source component (see
top left panel in \Fig{model}). This is consistent with previous results
reported by \citet{Brewer08a}, who find an optically faint companion
(component F in their paper) $\sim$2.4\,kpc away from the AGN host galaxy,
and C06, who find evidence for an interacting galaxy near RXJ1131.
Spatially, the red velocity component of the CO emission
also coincides with this component F. It is therefore evident that we
detect \bco emission in the companion galaxy.
To quantify the type of merger (major v.s. minor) conventionally with a mass
ratio, we decompose the total line flux into two components:
one from RXJ1131 and the other from its companion.
Since the companion is only detected in the red-most channel, we
use the best-fit flux densities and magnification factors obtained
from the model of this channel to derive the intrinsic gas mass in the companion.
Assuming a brightness temperature ratio of $r_{\rm 21}$\,=\,1 and
a CO luminosity-to-H2 mass conversion factor of
\alphaco\,=\,0.8 (K \kms pc$^2$)\pmOne, we find 
a molecular gas mass of $M_{\rm gas}$\,=\,$($1.92\pmm0.09$)$\,\E{9} \Msun. 
%statistical unc. only (i.e. draw from distributions of on mag. factor & intrinsic flux)
For the molecular gas mass in RXJ1131, we derive
its intrinsic line flux over the FWZI linewidth
using the respective magnification
factors listed in \Tab{model}, which to
first order takes into account effect of differential lensing.
This yields $I_{\small \bco}$\,=\,2.93\pmm0.70 Jy\,\kms,
where the uncertainty includes those on
the magnification factors.
Adopting the same brightness temperature ratio and \alphaco\ as
used for the companion, this corresponds to a gas mass of
$M_{\rm gas}$\,=\,$($1.38\pmm0.33$)$\,\E{10} \Msun,
implying a gas mass ratio of $\sim$7:1 between RXJ1131 and its companion.
We thus classify the system to be a ``wet-wet'' minor merger according to
the classification scheme commonly used in literature.

@@

\subsubsection{Spatial Extent and Differential Lensing} \label{sec:differential}
In the image plane shown in  \Fig{CO21mom}, the redshifted component is 
cospatial with the Einstein Ring seen in the
optical image, with most of its apparent flux originating from the lensed arc
in the southeast, whereas the blue component is predominately coming from
solely the lensed arc. To further illustrate this, we show the
channel maps of 21.5\,\kms width and a spatial spectra map of 1\farcs5 resolution in
\Fig{chanmap} and \Fig{spatialSpec}, respectively. The figures
show that emission
is present to the west, peaking toward the lensing arc (black crosses in
\Fig{chanmap}) in the red wing, and shifts to the east with decreasing velocity
(blue wing).
This is consistent with the source plane positions in our models and 
is suggestive of an extended CO emitting region.

@@

\subsection{\bco Dynamical Modeling} \label{sec:dynamics} %DONE
Assuming the velocities of the respective channels used in the
lens modeling correspond to solely the tangential component of the
true velocity vector of a rotating disk (i.e., along the major axis),
we extract a one dimensional PV diagram in \Fig{PV}
by slicing across their source plane positions (PA: 121\degr).

@@

In the rest-frame, 
emission in the observed $H$-band corresponds to NIR emission, 
tracing radiation from the accretion disk surrounding
the central AGN and also from old and evolved stellar populations; 
$I$-band corresponds to roughly the optical $V$-band, tracing stellar radiation from
existing, less massive (\ie longer-lasting) stars;
$V$-band corresponds to roughly $U$-band,  tracing radiation from massive young stars 
in the host galaxy. Hence,
the $V$-band compactness may be explained in part
due to the fact that its emission is
more susceptible to dust extinction than in other bands and/or 
a central starburst caused by higher 
concentrations of star-forming gas towards the central regions -- owing to
gravitational perturbations induced
from interactions with the companion
\citep[\eg][]{DiMatteo05a}.
The rest-frame NIR emission is likely to be
dominated by evolved stars since 
the AGN is located at $\sim$0\farcs016 inside the central region % and R_H is 7 kpc
of the host galaxy \citep{Sluse06a}, implying a compact accretion disk. 
This is consistent with the picture that old stars form first and constitute the bulge component  
of a spiral galaxy and that nuclear starbursts (in the inner few kpc) are triggered in mergers.

% assuming virialized gas
%Using $V_{\rm rot}$ estimate from the modeling, we find a dynamical mass of
%$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 17\E{10}\,\Msun enclosed
%within the CO-emitting region. If we instead consider the
%\bco line peak separation $(\Delta v_{\rm sep}/2 \sim$200\,\kms$)$ as the rotation velocity, we find
%$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 5.8\E{10}\,\Msun.
%We correct for the inclination effect using the
%morphological axial ratio ($a/b\sim$1\farcs8 / 3\farcs25) 
%from the reconstructed image (Figure 3 in C06), yielding
%an inclination angle of 56.4\degr, which is consistent with the
%observed unobscured AGN and an observable double peak line profile.
%The dynamical mass is then
%8.3\E{10}\Msun\,$<$\,$M_{\rm dyn}$($<$6\,kpc)\,$<$\,25\E{10}\Msun.
%Since this quantity is derived under the assumption that the gas is
%virialized, which is highly unlikely given the velocity dispersion and the
%presence of a close companion, our estimate is
%at most an upper limit.

%% using disk model
Using $M_{\rm dyn}$\,$\sin^2 i$ = 4\E{4}\,$v_{\rm FWHM}^2\,R$
 \citep{Neri03a}, which assumes a disk geometry,  and our estimate of $V_{\rm rot}$ as 
$v_{\rm FWHM}$, we find a dynamical mass of
$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 3\E{10}\,\Msun enclosed
within the CO-emitting region. 
If we instead consider the
\bco line peak separation $(\Delta v_{\rm sep}/2 \sim$200\,\kms$)$ as the rotation velocity, we find
$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 1\E{10}\,\Msun.
To correct for the inclination effect, we
infer an inclination angle of 56.4$\degr$ using
the morphological axial ratio ($a/b\sim$1\farcs8 / 3\farcs25) 
from the reconstructed image (Figure~3 in C06). This inclination angle 
is consistent with the
observed unobscured AGN and an observable double peak line profile.
The dynamical mass is then
1.4\E{10}\Msun\,$<$\,$M_{\rm dyn}$($<$6\,kpc)\,$<$\,4.3\E{10}\Msun.
% the systematic uncertainty on the inclination angle may cause this estimate to differ by 
% a factor of $\sim$2.
Our estimate is likely a lower limit given the presence of a companion. In a merger model, 
the dynamical mass would be a factor of $\sim$2 higher \citep[and references therein]{Neri03a}.

\subsection{SED Modeling} \label{sec:SED}  % DONE
We fit dust SED models to the
24\,\micron$-$2.2\,mm photometry in \Fig{SED}, where we also
include the IRAS 60\,$\micron$ and 100\,$\micron$ upper limits
to constrain the dust peak.
The fit is performed with the code
\ncode{mbb\_emcee} \citep[\eg][]{Riechers13a,Dowell14a}, which samples the posterior
using an MCMC approach and uses instrumental
response curves to perform color correction on-the-fly.
The SED model consists of a modified-blackbody
function with a power-law attached to the
Wien side to account for an excess in the MIR owing to warm,
small dust emission.
% Previous studies find that in the absence of mid-IR data, a powerlaw slope
% of $\alpha$ = 2 is consistent with SB and slightly more shallow, $\sim$1.5, % for SB/AGN composite systems (Blain et al., 2003; Casey, 2012; Koss et al., 2013).
%
%We add $\sim$15\% calibration uncertainties in quadrature to obtain the total
%uncertainties for the PdBI continuum in our fitting procedure.
The model is thus described by five free parameters: the rest-frame characteristic dust
temperature (T$_{d}$), the emissivity index ($\beta$), the power-law index
($\alpha$), the flux normalization at 500\,$\micron$ ($f_{\rm norm}$), and
the observed-frame wavelength at which the emission
becomes optically thick ($\lambda_{0}$). We impose
an upper limit of 100\,K on $T_d$ \citep[see \eg][]{Sajina12a}, 
a Gaussian prior centered around
$\mu$\,=\,1.9 with $\sigma$\,=\,0.3 on $\beta$, and an upper limit of
1000\,$\micron$ on $\lambda_0$.
We check for chain convergence by requiring the autocorrelation
length of each parameter to be less than the number of steps
taken for the burn-in phase (which are then discarded).
Here we report the statistical means % modes in log file
% summary statistics (global mode (where min. chi),
% marginal mode (in log file), posterior median (instead of posterior means;
% need to compute)
and the 1$\sigma$ confidence interval in the marginal PDFs
as the best-fit parameters, as listed in \Tab{SED}.

@@

\subsection{Gas Properties} \label{sec:properties}
In this section, we derive the gas properties of the merger system
based on \bco and compare with those reported by
C13, which is the largest sample of
IR-luminous galaxy at similar redshift
(0.6\,$<$\,$z$\,$<$\,1.0) with CO measurements\footnote{The
\fir luminosity in C13 is derived based on 60\,$\micron$ and 100\,$\micron$ IRAS fluxes,
and using a different definition of
\LFIR: rest-frame 40\,$-$\,500\,\micron. Following this convention, 
we find a \fir luminosity of 
\LFIR = $($8.8\pmm0.4$)$\E{11}$(\mu_{\rm L}$/5.5$)\pmOne$\,\Lsun and
a SFR of $($150\pmm 70$)$\,\sfrU.}.
% the SFR of RXJ1131 is lower (cf. SFR\,$>$\,200 \Msun yr\pmOne, with an average of 1200 in C13).
We note that their results are based on \bco and \rot{4}{3} line observations with the 
IRAM 30-m single-dish telescope.

\subsubsection{Linewidth and Sizes} 
FWHM from single gauss fit?
We find that the linewidths for both components (redshifted and blueshifted)
inferred from a double Gaussian fit to the line profile are
comparable to the C13 ULIRG sample
($\Delta v_{\rm FWHM}$ of 370\,\kms) and local ULIRGs
(300\pmm85\,\kms; \citealt[][]{Solomon97a}).
The CO gas in RXJ1131 is
distributed $\sim$6\pmm3\,kpc in radius across (in
the source plane), which is more extended than the
sample of disk-like U/LIRGs studied by
\citet[hereafter U14]{Ueda14a}, % also classified U/LIRG using FIR from 60, 100 micron measurements
who find an average radius of 3.5\,$\pm$\,2.3\,kpc
with a range spanning 1.1\,$-$\,9.3\,kpc.
% This is expected if the positive correlation in the linewidth-size relation
% holds at intermediate redshifts. Yet we cannot quantify this further
% with the data represented in this paper.
COMPARE WITH DOWNES SOLOMON98

\subsubsection{Gas Mass and Gas Ratios}
Using the lensing-corrected molecular gas mass of  
$M_{\rm gas}$\,=\,$($1.38\pmm0.33$)$\E{10}\,\Msun in RXJ1131 and
$($1.92\pmm0.09$)$\E{9}\,\Msun in its companion derived in \Sec{caveat}, 
a total molecular gas mass of $M_{\rm gas}^{\rm total}$\,=\,$($1.57\pmm0.38$)$\E{10}\,\Msun is 
residing within the merger system. 
This is comparable to the
C13 sample ($M_{\rm gas}$\,=\,1.5\E{10}\Msun) as well as
local U/LIRGs \citep{Solomon97a, Sanders96a} but higher than
in local LIRGs (U14).

% gas-to-dyn ratio
Using a dynamical mass of BLAH and the total gas mass ($M_{\rm gas}^{\rm total}$),
we find a gas-to-dynamical mass fraction of $f_{\rm gas-dyn}$\,=\,BLAH.
% gas to dust ratio:
Using the dust mass derived from SED fitting,
we find a gas-to-dust ratio of BLAH\pmm
BLAH, which is consistent with
the C13 sample ($f_{\rm gas-dust}$\,=\,206) and local U/LIRGs
(200$-$350; \citealt{Sanders91a}, Contini \& Contini 2003; Seaquist et al. 2004; Wilson et al. 2008).
